%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\usepackage{hyperref}
\usepackage{fontawesome5} % For Font Awesome icons
\usepackage{amssymb}      % For additional symbols

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    pdftitle={Tirtho Roy Resume},
    pdfpagemode=FullScreen,
}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{TIRTHO ROY}

\begin{document}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL LINKS SECTION
%----------------------------------------------------------------------------------------
\noindent
\makebox[\textwidth][s]{%
    \textbf{Senior / Graduate} \hfill
    \href{https://www.linkedin.com/in/tirtho-roy-apon}{\faLinkedin\ Tirtho-Roy} \hfill
    \href{https://scholar.google.com/citations?user=v1y3XMUAAAAJ&hl=en&authuser=1}{\texttt{Tirtho-Roy}} \hfill
    \href{https://github.com/tirtho149}{\faGithub\ tirtho149} \hfill
    \href{mailto:tirtho@iastate.edu}{\faEnvelope\ tirtho@iastate.edu}}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Science in Data Science} \hfill {Aug 2023 – Present} \\
Iowa State University, Ames, IA 

% Add any other relevant educational information
{\bf Master’s of Science in Mechanical Engineering  } \hfill {Jan 2025 – Present} \\
Iowa State University, Ames, IA 

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCE}

\begin{rSubsection}{Undergraduate Research Assistant}{Apr 2024 – Present}{Translational AI Center, Iowa State University}{} 
\item Collaborating with Professor Soumik Sarkar on leveraging LLMs in finance to enhance decision-making processes.
\item Gaining insights into AI integration in financial applications, and developing advanced skills in machine learning.
\end{rSubsection}

\begin{rSubsection}{Undergraduate Software Developer}{June 2024 – December 2024}{Iowa State University Department of Agricultural and Biosystems Engineering}{} 
\item Worked with Professor Ryan McGhee on developing a versatile chatbot frontend to improve UI and experience.
\item Engaged in software development and user interface design.
\end{rSubsection}

\begin{rSubsection}{Undergraduate Research Volunteer}{Apr 2024 – May 2024}{ISU Department of Computer Science}{} 
\item Explored the behavior of large language models with knowledge conflicts under Professor Qili's guidance.
\item Developed key skills in data research and analysis.
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	PUBLICATIONS & PRESENTATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PUBLICATIONS \& PRESENTATIONS}

\textbf{Federated In-Context Prompt Selection for Multi-Modal 3D Dental Imaging: A Theoretical Framework with Privacy-Preserving Guarantees} \\
ODIN 2025 (Oral and Dental Image aNalysis) Workshop @ MICCAI 2025 (29th International Conference on Medical Image Computing and Computer Assisted Intervention), Poster
\begin{itemize}
    \item Developed a novel federated learning framework for multi-modal 2D and 3D dental imaging with privacy-preserving guarantees.
    \item Key contributions: cross-modal prompt alignment, hierarchical multi-modal optimization, and Byzantine-resilient aggregation with differential privacy.
\end{itemize}

\textbf{LLM-based Insights into How Market Orientation and Brand Storytelling Affect Investors' Evaluation of Startup Pitches} \\
REU Summer Symposium 2025, Poster; TrAC Day 2025, Poster \& Flash Talk
\begin{itemize}
    \item Presented research poster at REU Summer Symposium 2025 while serving as a peer mentor to Taj Singh, enhancing both academic and personal growth within the Translational AI Center.
    \item Delivered a flash talk at TrAC Day 2025, exploring how passion, responsiveness, and storytelling drive investor decisions using GPT-4o and Shark Tank data.
\end{itemize}

\textbf{Enhancing Medical AI Safety Through Multi-Agent Evaluation and Iterative Refinement} \\
The 16th ACM Conference on Bioinformatics, Computational Biology, and Health Informatics (ACM-BCB) 2025, Pennsylvania, USA, Poster
\begin{itemize}
    \item Developed a novel multi-agent refinement framework to enhance the ethical, safety, and regulatory compliance of medical LLM outputs.
    \item Framework pairs DeepSeek R1 and Med-PaLM as generative models with LLaMA 3.1 and Phi-4 as evaluator agents, iteratively refining responses against the American Medical Association's nine Principles (AMA-9) and a five-tier Safety Risk Assessment (SRA-5).
    \item Strengthened reliability and alignment of medical LLM outputs, addressing real-world deployment challenges.
\end{itemize}

\textbf{LlamaHealth: Assessing LLaMA's Performance in Multi-Class Healthcare Test Result Prediction} \\
ICERIE 2025, Shahjalal University of Science and Technology, Sylhet, Bangladesh, Poster
\begin{itemize}
    \item Earned Certificate of Participation; reinforced focus on responsible AI for healthcare.
    \item Investigated LLaMA's multi-class prediction capabilities in healthcare datasets.
\end{itemize}

\textbf{Benchmarking Bioemu-1: Establishing a Baseline for Protein Structural Ensemble Prediction} \\
AIChE Annual Meeting 2025, Boston, USA, Poster
\begin{itemize}
    \item Presented in the Computational Molecular Science and Engineering Forum poster session.
\end{itemize}

\textbf{Leveraging Vision Language Models for Specialized Agricultural Tasks} \\
Proceedings of the 2025 IEEE/CVF Winter Conference on Applications of Computer Vision (WACV)
\begin{itemize}
    \item Explored how vision-language models improve performance on specialized agricultural benchmarks.
\end{itemize}

\textbf{The Impact of Market Orientation and Brand Storytelling on Shark Tank Evaluations} \\
Journal of Business \& Industrial Marketing (JBIM)
\begin{itemize}
    \item Analyzed how storytelling and market orientation influence investor evaluation using LLM analysis.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	INTERNSHIP/TRAININGS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{INTERNSHIPS}

\textbf{Undergraduate Summer Research Intern – Translational AI Center} \hfill May 2024 - July 2024

\end{rSection}
%----------------------------------------------------------------------------------------
%	HONORS & AWARDS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{HONORS \& AWARDS}

\textbf{Dean's High Impact Award for Undergraduate Research} (Fall 2025)
\begin{itemize}
    \item Recognized for outstanding contributions to undergraduate research at Iowa State University.
    \item Highlighted for innovation and rigor in research area/project.
    \item Mentored or collaborated with peers to enhance research outcomes.
\end{itemize}

\textbf{Dean's List} (Fall 2024)
\begin{itemize}
    \item Achieved distinction for academic excellence across all courses.
    \item Maintained high GPA while engaging in research and extracurricular activities.
\end{itemize}

\textbf{Best-In-Show, George Washington Carver Poster Challenge} (2025)
\begin{itemize}
    \item Awarded top recognition for research poster presentation at the annual Carver Poster Challenge.
    \item Selected from participants based on clarity, impact, and originality of research.
\end{itemize}

\textbf{Borlaug Poster Competition} (2025)
\begin{itemize}
    \item Developed research under TrAC – Translational AI Center exploring how AI and FinTech empower entrepreneurs addressing global food and sustainability challenges.
    \item Recognized as Undergraduate division 1st place by Iowa State University College of Agriculture and Life Sciences for connecting technology, entrepreneurship, and global food systems.
\end{itemize}

\textbf{Bangladesh–Sweden Trust Fund Travel Grant} (2025)
\begin{itemize}
    \item Competitive international grant supporting research travel and presentation opportunities.
    \item Enabled participation in conference/seminar/workshop and networking with global researchers.
\end{itemize}

\textbf{ISU LAS Travel Grant} (\$400, AIChE 2025)
\begin{itemize}
    \item Awarded by the College of Liberal Arts and Sciences, Iowa State University.
    \item Supported conference presentation at AIChE 2025 and engagement with leading experts.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	ACADEMIC SERVICE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{ACADEMIC SERVICE}

\textbf{Reviewer}, LatinX in Computer Vision Workshop @ CVPR 2025
\begin{itemize}
    \item Reviewed submissions focused on computer vision applications and methodologies.
    \item Emphasized promoting diversity and representation in AI research.
\end{itemize}

\textbf{Reviewer}, Second Workshop on Bangla Language Processing (BLP) @ IJCNLP-AACL 2025
\begin{itemize}
    \item Reviewed submissions for the workshop co-located with IJCNLP-AACL 2025 in Mumbai, India.
    \item Contributed to advancing natural language processing research for Bangla language.
\end{itemize}

\textbf{Reviewer}, LatinX in AI (LXAI) Workshop @ NeurIPS 2025
\begin{itemize}
    \item Evaluated papers and workshop submissions at prominent AI conference.
    \item Supported efforts to advance inclusion and emerging research within the AI community.
\end{itemize}

\textbf{Ethics Reviewer}, NeurIPS 2025 Datasets and Benchmarks Track
\begin{itemize}
    \item Served as an ethics reviewer for dataset and benchmark papers.
    \item Ensured compliance with ethical research practices and responsible AI deployment.
\end{itemize}

\end{rSection}

\end{document}